%!TEX root = main.tex
\addcontentsline{toc}{section}{参考文献}
\begin{thebibliography}{99}
  \bibitem{key1} 著者名，“標題，”雑誌名，巻，号，pp.を付けて始め-終りのページ，月年.
Author name, “Title,” Journal title, volume, issue, Start-End page with pp., Month Year.

  \bibitem{key2} 山上一郎，山下二郎，“パラメトリック増幅器，”信学論 (B), vol.J62-B, no.1, pp.20-27, Jan. 1979.
I. Yamagami and J. Yamashita, “Parametric amplifier,” IEICE Trans. Commun. (Japanese Edition), vol.J62-B, no.1, pp.20-27, Jan. 1979.
  \bibitem{key3} W. Rice, A.C. Wine, and B.D. Grain, “Diffusion of impurities during epitaxy,” Proc. IEEE, vol.52, no.3, pp.284-290, March 1964.
  \bibitem{key4} 著者名，書名，編者名，発行所，発行都市名，発行年.
Author name, Book title, Editor name, Publisher, Issuing City name, Year of issue.
  \bibitem{key5} 山田太郎，移動通信，木村次郎（編），（社）電子情報通信学会，東京，1989.
T. Yamada, Mobile communication, J. Kimura (ed.), IEICE, Tokyo, 1989.
  \bibitem{key6} H. Tong, Nonlinear Time Series: A Dynamical System Approach, J.B. Elsner, ed., Oxford University Press, Oxford, 1990.
  \bibitem{key7} 著者名，“標題，”書名，編者名，章番号またはpp.を付けて始め-終りのページ，発行所，発行都市名，発行年．
Author name, “Title,” Book title, Editor name, Chapter number or Start-End page with pp., Publisher, Issuing City name, Year of issue.
  \bibitem{key8} 山田太郎，“周波数の有効利用，”移動通信，木村次郎（編），pp.21-41，（社）電子情報通信学会，東京，1989.
T. Yamada, “Effective use of frequency,” Mobile communication, J. Kimura (ed.), pp.21-41, IEICE, Tokyo, 1989.
  \bibitem{key9} H.K. Hartline, A.B. Smith, and F. Ratlliff, “Inhibitory interaction in the retina,” in Handbook of Sensory Physiology, ed. M.G.F. Fuortes, pp.381-390, Springer-Verlag, Berlin, 1972.
  \bibitem{key10} 著者名，“標題，”会議名，no.を付けて論文番号，pp.を付けて始め-終りのページ，開催都市名，国名，月年．
Author name, “Title,” Conference name, Article number with no., Start-End page with pp., Host city name, Country of issue, Month Year.
  \bibitem{key11} 川上三郎，川口四郎，“紫外域半導体レーザ，”1995信学全大，分冊2, no.SB2-1, pp.20-21，東京，日本，Sept. 1995.
S. Kawakami and S. Kawaguchi, “Ultraviolet semiconductor laser,” Proc. IEICE Gen. Conf. 1995, I\hspace{-1.2pt}I, no.SB2-1, pp.20-21, Tokyo, Japan, Sept. 1995.
  \bibitem{key12} 著作権管理委員会，“電子情報通信学会著作権規程，”電子情報通信学会，https://www.ieice.org/jpn/about/kitei/chosakukenkitei.pdf, 参照Aug. 3, 2009.
IEICE Copyright Management Committee, “IEICE Provisions on Copyright,” IEICE, https://www.ieice.org/jpn/about/kitei/chosakukenkitei.pdf, ref. Aug. 3, 2009.
\end{thebibliography}